Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-27 paper/main.tex
Moved something and wrote two more words.

Tahoe has a three layer architecture: the key-value store, the filesystem, and
the application.

@@

\subsection{Related technologies}

Tahoe-\ac{LAFS} uses a number of techniques to realize the functionality
needed by a secure, distributed filesystem.

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashing.pdf}
    \caption{Tahoe-LAFS: Location of hashing}
    \label{fig:tahoehashing}
\end{figure}

>>>>

Tahoe has a three layer architecture: the key-value store, the filesystem, and
the application \cite{t_tahoe}.

@@

\paragraph{File types.}

There are two kinds of files in the Tahoe-\ac{LAFS} -- \textbf{immutable} and
\textbf{mutable} files.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashing.pdf}
    \caption{Tahoe-LAFS: Location of hashing.}
    \label{fig:tahoehashing}
    \emph{Figure from
     \href{http://tahoe-lafs.org/source/tahoe/trunk/docs/specifications/mut.svg}
     {tahoe-lafs.org}}
\end{figure}

@@

\paragraph{Encryption key.}

\paragraph{Ciphertext and shares.}

Stored in Capability/URI Extension Block.
URI Extension Block $=$ Root hash $+$ file size $+$ encoding parameters.
URI / File read cap = Hash of UEB $+ K_c$

\paragraph{Storage Index.}

file-encoding1.svg
